%-------------------------
% Resume
% Author : Mark Ortleb
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{2pt}}
	}
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
	\begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\href{https://github.com/markortleb}{\Large Mark Ortleb}} & Email : \href{mailto:markortleb@gmail.com}{markortleb@gmail.com}\\
		\href{https://github.com/markortleb}{https://github.com/markortleb} & Mobile : \href{tel:+17202196444}{+1-720-219-6444} \\
	\end{tabular*}
	
	
	%-----------EDUCATION-----------------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{Metropolitan State University of Denver}{Denver, CO}
	{Bachelor of Science in Applied Mathematics;  GPA: 3.49}{Aug. 2014 -- May. 2018}
	\resumeSubHeadingListEnd
	
	
	%-----------EXPERIENCE-----------------
	\section{Experience}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{Dice.com}{Denver, CO}
	{Data Engineer}{Nov 2021 - Present}
	\resumeItemListStart
	\resumeItem
	{Maintained the Airflow data ingestion processes and responded to issues as needed.}
	\resumeItem
	{Migrated legacy data to be presented in the Data Warehouse using dbt.}
	\resumeItem
	{Conducted end to end data modeling, by working with other teams within the organization to understand the business value of data that would be presented in the Redshift Data Warehouse.}
	\resumeItem
	{Changed non-Type-2 dimensional models into Type-2 slowly changing dimensions, such that changes to a record are reflected, thus enabling as-is/as-was reporting.}
	\resumeItemListEnd
	
	
	\resumeSubheading
	{Shaw Communications}{Denver, CO}
	{Big Data Developer}{Mar 2019 - Nov 2021}
	\resumeItemListStart
	\resumeItem
	{Created and maintained ETL pipelines, which were mostly written with PySpark or Hive on EMR.}
	\resumeItem
	{Troubleshooted and resolved data related issues. This included answering alerts, and analyzing/fixing the tables in S3 for various data quality issues.}
	\resumeItem
	{Unified customer data between Shaw Communications and it's subsidiary, Freedom Mobile, by using PySpark to pull records from the Snowflake Data Warehouse, perform transformations, and load the transformed records to ElasticSearch.}
	\resumeItem
	{Assisted another team with the development of an API that loads posted records to an SQS Queue, which would then trigger a Lambda function to transform batches of data, and send it to an external database. The CICD infrastructure was setup using the Serverless Framework.}
	\resumeItemListEnd
	
	\resumeSubheading
	{Scott's Liquid Gold}{Denver, CO}
	{Computer Programmer}{Jun 2018 - Mar 2019}
	\resumeItemListStart
	\resumeItem
	{Maintained the integrity of business and system processes on the self hosted IBM i mid-range computer.}
	\resumeItem
	{Completely overhauled the legacy month-end process to a stable and reliable state.}
	\resumeItem
	{Designed a "client side" business application for Windows machines using C++ and the Win32 API, which allowed users to drag and drop from a list of products and load a new inventory list back to the IBM i database.}
	\resumeItem
	{Developed an RPG IV program on the IBM i to mark-up and style "bill of lading" documents, which would automatically be sent to a printer in the shipping department upon order submission.}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	
	
	%--------PROGRAMMING SKILLS------------
	\section{Technologies}
	  \resumeSubHeadingListStart
	    \item{
		      \textbf{Programming Languages}{: Python, JavaScript, C++, Java}
		    }
	    \item{
	    	\textbf{Databases}{: Redshift, Snowflake, DynamoDB, ElasticSearch}
	    }
	    \item{
	    	\textbf{Data Tools}{: dbt, SQL, Spark, Hive}
	    	}
    	\item{
    		\textbf{AWS Tools}{: S3, Glue, Athena, EMR, API Gateway, CloudFormation, CodeBuild}
    	}
    	\item{
    		\textbf{Other Tools}{: Docker, HTML, CSS, Airflow}
    	}
    	
	  \resumeSubHeadingListEnd
	
	
	%-------------------------------------------
\end{document}